---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# intercept

Messages and warnings are sometimes hard to debug because there's no simple
way to know where they occur. {intercept} provides some helpers to trigger behaviors
conditionally depending on the class of the condition, the actual message, or the
package where it occurs.

* `suppress_warnings()` / `suppress_messages()` remove only warnings and messages that qualify
* `abort_on_warnings()` / `abort_on_messages()` fail on relevant warnings/messages only,
  a bit like `options(warn = 2)` but restricted in scope
* `with_verbose_warnings()` / `with_verbose_messages()` print the error class and the trace where
relevant warnings/messages occur
* `recover_on_warnings()` / `recover_on_messages()` let you enter the debugger in a chosen frame
 when a relevant warning/message occurs 

## Installation

You can install the development version of intercept like so:

``` r
devtools::install_github("moodymudskipper/intercept")
```

## Example

```{r, error = TRUE}
library(intercept)
library(dplyr, warn.conflicts = FALSE)
fun <- function() {
  left_join(tibble(a = 1, b = 2), tibble(a = 1, c = 3))
}

# triggers a message because of implicit join column choice
fun()

# just like suppressMessage() by default
suppress_messages(fun())

# doesn't qualify, message is not suppressed
suppress_messages(fun(), endsWith, "Joining")

# qualifies
suppress_messages(fun(), startsWith, "Joining")

# we can use regular expressions
suppress_messages(fun(), "w.th")

# or packages
suppress_messages(fun(), .packages = "dplyr")

# abort selectively, same arguments
abort_on_messages(fun(), .packages = "dplyr")
```

we can print additional info about messages or warnings, conditionally if we want,
here without any condition

```{r, eval = FALSE}
fun2 <- function() {
  left_join(tibble(a = c(1,1), b = 2), tibble(a = c(1,1), c = 3), by = "a")
}

with_verbose_warnings(fun2())
#> warning of class <dplyr_warning_join_relationship_many_to_many/dplyr_warning_join/dplyr_w#> arning/rlang_warning/warning/condition>
#> Detected an unexpected many-to-many relationship between `x` and `y`.
#>      ▆
#>   1. ├─intercept::with_verbose_warnings(fun2())
#>   2. │ └─intercept:::with_condition(...) at intercept/R/with_verbose.R:22:2
#>   3. │   └─base::withCallingHandlers(.expr, warning = handler0) at #> intercept/R/with_condition.R:20:4
#>   4. ├─global fun2() at intercept/R/with_verbose.R:22:2
#>   5. │ ├─dplyr::left_join(...)
#>   6. │ └─dplyr:::left_join.data.frame(...)
#>   7. │   └─dplyr:::join_mutate(...)
#>   8. │     └─dplyr:::join_rows(...)
#>   9. │       └─dplyr:::dplyr_locate_matches(...)
#>  10. │         ├─base::withCallingHandlers(...)
#>  11. │         └─vctrs::vec_locate_matches(...)
#>  12. ├─vctrs:::warn_matches_relationship_many_to_many(...)
#>  13. │ └─vctrs:::warn_matches_relationship(...)
#>  14. │   └─vctrs:::warn_matches(...)
#>  15. │     └─vctrs:::warn_vctrs(...)
#>  16. │       └─rlang::warn(...)
#>  17. │         └─base::warning(cnd)
#>  18. │           └─base::withRestarts(...)
#>  19. │             └─base (local) withOneRestart(expr, restarts[[1L]])
#>  20. │               └─base (local) doWithOneRestart(return(expr), restart)
#>  21. ├─dplyr (local) `<fn>`(`<vc______>`)
#>  22. │ └─dplyr:::rethrow_warning_join_relationship_many_to_many(cnd, error_call)
#>  23. │   └─dplyr:::warn_join(...)
#>  24. │     └─dplyr:::warn_dplyr(...)
#>  25. │       └─rlang::warn(...)
#>  26. │         └─base::warning(cnd)
#>  27. │           └─base::withRestarts(...)
#>  28. │             └─base (local) withOneRestart(expr, restarts[[1L]])
#>  29. │               └─base (local) doWithOneRestart(return(expr), restart)
#>  30. └─intercept (local) `<fn>`(`<dp______>`)
#>  31.   └─intercept (local) handler(cond) at intercept/R/with_condition.R:13:6
#> # A tibble: 4 × 3
#>       a     b     c
#>   <dbl> <dbl> <dbl>
#> 1     1     2     3
#> 2     1     2     3
#> 3     1     2     3
#> 4     1     2     3
#> Warning message:
#> In left_join(tibble(a = c(1, 1), b = 2), tibble(a = c(1, 1), c = 3),  :
#>   Detected an unexpected many-to-many relationship between `x` and `y`.
#> ℹ Row 1 of `x` matches multiple rows in `y`.
#> ℹ Row 1 of `y` matches multiple rows in `x`.
#> ℹ If a many-to-many relationship is expected, set `relationship = "many-to-many"` to #> silence this warning.

# we can remove messages or warnings depending on class too
suppress_warnings(fun2(), .classes = "dplyr_warning_join")
#> # A tibble: 4 × 3
#>       a     b     c
#>   <dbl> <dbl> <dbl>
#> 1     1     2     3
#> 2     1     2     3
#> 3     1     2     3
#> 4     1     2     3
```

Enter the debugger conditionally:

```{r, eval = FALSE}
recover_on_messages(fun(), startsWith, "Joining")
#> message of class <rlang_message/message/condition>
#> Joining with `by = join_by(a)`
#> 
#> Enter a frame number, or 0 to exit   
#> 
#>  1: recover_on_messages(fun(), startsWith, "Joining")
#>  2: recover.R#9: with_condition(.expr, "message", handler, .f, ..., .cla
#>  3: with_condition.R#18: withCallingHandlers(.expr, message = handler0)
#>  4: with_condition.R#18: fun()
#>  5: #2: left_join(tibble(a = 1, b = 2), tibble(a = 1, c = 3))
#>  6: left_join.data.frame(tibble(a = 1, b = 2), tibble(a = 1, c = 3))
#>  7: join_mutate(x = x, y = y, by = by, type = "full", suffix = suffix, n
#>  8: join_by_common(x_names, y_names, error_call = error_call)
#>  9: inform(glue("Joining with `by = join_by({by_names})`"))
#> 10: withRestarts(muffleMessage = function() NULL, {
#>     signalCondition(c
#> 11: withOneRestart(expr, restarts[[1]])
#> 12: doWithOneRestart(return(expr), restart)
#> 13: signalCondition(cnd)
#> 14: (function (cond) 
#> {
#>     msg <- cli::ansi_strip(conditionMessage(cond))
#> 
#> 15: with_condition.R#13: handler(cond)
#> 
#> Selection: 
```
